Holomorphic field theories and higher algebra

### 2023-08-15 highervertexops.tex
merge

The model $\sfA$ for algebraic functions on punctured affine space was constructed using the ring
\beqn
\sfR = \C[z_i,\lambda_i] \slash (z_i \lambda_i = 1) .
\eeqn
Let $\Hat{\sfR}$ denote the completion of this ring with respect to the ideal generated by $z_1,z_2$.
So I think
\beqn
\Hat{\sfR} = \C[[z_i]][\lambda_i] \slash (z_i \lambda_i) .
\eeqn

Let $\Hat{A}$ be the graded algebra free generated over $\Hat{\sfR}$ and the degree one variable $\omega$.
The cohomology of $(\sfA, \dbar)$ is $\C[[z_i]]$ in degree zero and $\C[\lambda_i]$ in degree one.

>>>>

The model $\sfA$ for algebraic functions on punctured affine space was constructed using the ring
\beqn
\sfR = \C[z_i,\lambda_i] \slash (z_i \lambda_i = 1) .
\eeqn
Let $\Hat{\sfR}$ denote the completion of this ring with respect to the ideal generated by $z_1,z_2$.
So I think
\beqn
\Hat{\sfR} = \C[[z_i]][\lambda_i] \slash (z_i \lambda_i=1) .
\eeqn

Let $\Hat{\sfA}$ be the graded algebra free generated over $\Hat{\sfR}$ and the degree one variable $\omega$.
The cohomology of $(\Hat\sfA, \dbar)$ is $\C[[z_i]]$ in degree zero and $\C[\lambda_i]$ in degree one.
